Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure15 labels

trimesh_removed_pbmc <- ggplot() + 
  geom_point(
    data = umap_pbmc_scaled_with_cluster,
    aes(
      x = UMAP1,
      y = UMAP2,
      color = cluster
    ),
    alpha = 0.2,
    size = 0.1#,
    #color = '#a65628'
  )  +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist6 <- tsne_mnist2 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#999999') +
  interior_annotation("f", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c", position = c(0.94, 0.92)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist5 <- pacmap_mnist |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e") +
  theme(aspect.ratio = 1)
```

>>>>

trimesh_removed_pbmc <- ggplot() + 
  geom_point(
    data = umap_pbmc_scaled_with_cluster,
    aes(
      x = UMAP1,
      y = UMAP2,
      color = cluster
    ),
    alpha = 0.2,
    size = 0.1#,
    #color = '#a65628'
  )  +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", c(0.08, 0.9), cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("a", c(0.08, 0.9)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist6 <- tsne_mnist2 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#999999') +
  interior_annotation("f", c(0.08, 0.9)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c", c(0.94, 0.92)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist5 <- pacmap_mnist |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("e", c(0.08, 0.9)) +
  theme(aspect.ratio = 1)
```
